---
title: "Wiki Honours - Overview of Data"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Kelly Tall"
date: "15/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data source

The honours data set was downloaded from   <https://honours.pmc.gov.au/honours/search>.

The award names selected were:
Dame of the Order of Australia
Knight of the order of Australia
Companion of the Order of Australia
Medal
Member
Officer

Dates of these awards ranged from XX to XX

The number of each award extracted in total 


The fields that were extracted for eachreord are:

An example fo the first XX records and the informatio held are:

Data Set creation process: 







When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
